---
title: "Coding Challenge"
author: "Sheltzer Lab"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    toc_depth: 3
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE}
library(tidyverse)
```

```{r, message=FALSE}
raw.samples <- read_tsv('data/brca_metabric/data_clinical_sample.txt', comment = '#')
raw.mutations <- read_tsv('data/brca_metabric/data_mutations.txt', comment = '#')
```

## Questions

1. In words, describe the two input data files? What is the format of each?
2. In words, describe what the two code blocks below do?
3. Based on this code, how would you preprocess the data to reduce code redundancy? How would you test your preprocessing?
4. How would you test if the different breast cancer subtypes differ in their TP53 mutation rate?
5. What would you change about this code? Do you see any bugs?

## Code

```{r}
raw.mutations %>%
  filter(Variant_Classification != 'Silent') %>%
  group_by(Hugo_Symbol) %>%
  summarize(n = n_distinct(Tumor_Sample_Barcode)) %>%
  slice_max(order_by = n, n = 10)
```

```{r}
raw.mutations %>%
  filter(Variant_Classification != 'Silent') %>%
  inner_join(
    raw.samples %>%
      select(SAMPLE_ID, CANCER_TYPE_DETAILED),
    by = c('Tumor_Sample_Barcode' = 'SAMPLE_ID')
  ) %>%
  group_by(Hugo_Symbol, CANCER_TYPE_DETAILED) %>%
  summarize(n = n_distinct(Tumor_Sample_Barcode), .groups = 'drop') %>%
  group_by(CANCER_TYPE_DETAILED) %>%
  slice_max(order_by = n, n = 1)
```
